2024 US Election Prediction

### 2024-11-03 paper/paper.qmd

In this study, we apply statistical models, including a linear model of Trump's percentage over time, to quantify changes in his support level. Additionally, we adjust for pollster variations to provide a more accurate reflection of his support trajectory across different sources. Our findings reveal both temporal trends and variability among pollsters, highlighting the complexities of interpreting polling data in a polarized political environment. These insights contribute to a better understanding of Trump’s standing and the potential outcomes in 2024.

>>>>

In this study, we apply statistical models, including a linear model and a Bayesian model for each of Trump's and Harris' of percentages over time, to quantify changes and make comparisons to his support level. Additionally, we adjust for pollster variations to provide a more accurate reflection of his support trajectory across different sources. Our findings reveal both temporal trends and variability among pollsters, highlighting the complexities of interpreting polling data in a polarized political environment. These insights contribute to a better understanding of Trump’s standing and the potential outcomes in 2024.
